---
title: "MOdeling Assingment"
author: "Group-5 {April Greenwood, Amiya Ranjan Sahoo, Caleb Call, Rob Sheehy}"
date: "March 21, 2026"
output:
  html_document:
    toc: yes

---

```{r global-options, include=FALSE}
knitr::opts_chunk$set(
  echo    = TRUE,
  warning = FALSE,
  message = FALSE
)
```

---

# 1. Introduction

This file evaluates different models to identify which leads are most likely to advance to the next sales step. The EDA established that manufacturing mode is the strongest predictor, followed by account tier, functional area of the contact, and seniority. Geography and industry showed weaker standalone effects but remain useful interaction features.

There are 3 differnet prections used in this file: Logistic Regression, XGBoost, and Random Forest. Outcomes are compared using AUC, accuracy, pecision, recall and F1

---

# 2. Import Libraries

```{r}

library(readr)
library(dplyr)
library(tidyr)
library(stringr)
library(forcats)
library(janitor)
library(lubridate)
library(caret)        
library(recipes) 
library(rsample)       
library(xgboost)       
library(randomForest)   
library(pROC)           
library(yardstick)    
library(ggplot2)
library(scales)
library(gridExtra)
library(gt)

theme_set(theme_minimal(base_size = 12))
set.seed(123)
```

---

# 3. Data Overview
This step includes creating a target variable, cleans misisng values, and extracts seniority from jobs. 

```{r}
# Load data 

qal_raw <- read_csv("Mastercontrol QAL Performance.csv") %>%
  clean_names()

cat("Dimensions:", nrow(qal_raw), "rows ×", ncol(qal_raw), "columns\n")
```

```{r}
#EDA data cleaning

qal <- qal_raw %>%

# Target variable
  mutate(
    progressed = if_else(next_stage_c %in% c("SQL", "SQO", "Won"), 1L, 0L)
  ) %>%
  
  mutate(
    acct_primary_site_function = replace_na(acct_primary_site_function, "Unknown"),
    acct_manufacturing_model   = replace_na(acct_manufacturing_model,   "Unknown"),
    contact_lead_title         = replace_na(contact_lead_title,         "Unknown")
  ) %>%

  mutate(
    title_lower = tolower(contact_lead_title),
    seniority = case_when(
      str_detect(title_lower, "chief|ceo|cfo|cio|cto|coo|president") ~ "C-Level",
      str_detect(title_lower, "vp|vice president")                   ~ "VP",
      str_detect(title_lower, "director|head")                       ~ "Director",
      str_detect(title_lower, "manager|lead")                        ~ "Manager",
      TRUE                                                            ~ "Other"
    )
  ) %>%

  mutate(
    function_band = case_when(
      str_detect(title_lower, "quality|qa|qc")                    ~ "Quality",
      str_detect(title_lower, "manufactur|production|plant")      ~ "Manufacturing",
      str_detect(title_lower, "operation|ops")                    ~ "Operations",
      str_detect(title_lower, "regulator|compliance")             ~ "Regulatory",
      str_detect(title_lower, "engineer|process")                 ~ "Engineering",
      TRUE                                                         ~ "Other"
    )
  ) %>%

  mutate(
    cohort_month = month(qal_cohort_date, label = TRUE, abbr = TRUE)
  ) %>%

  select(-qal_id, -contact_lead_id, -next_stage_c,
         -contact_lead_title, -title_lower, -qal_cohort_date)

qal <- qal %>%
  mutate(
    progressed             = factor(progressed, levels = c(0, 1),
                                    labels = c("No", "Yes")),
    solution_rollup        = factor(solution_rollup),
    acct_target_industry   = factor(acct_target_industry),
    acct_manufacturing_model = factor(acct_manufacturing_model),
    acct_primary_site_function = factor(acct_primary_site_function),
    acct_tier_rollup       = factor(acct_tier_rollup),
    acct_territory_rollup  = factor(acct_territory_rollup),
    last_tactic_campaign_channel = factor(last_tactic_campaign_channel),
    priority               = factor(priority),
    seniority              = factor(seniority),
    function_band          = factor(function_band),
    cohort_month           = factor(cohort_month)
  )

cat("Target distribution:\n")
print(prop.table(table(qal$progressed)))

glimpse(qal)
```

---

# 4. Train / Test Split

Data is split into 70% training and 30% testing

```{r}
split_obj  <- initial_split(qal, prop = 0.70, strata = "progressed")
train_data <- training(split_obj)
test_data  <- testing(split_obj)

cat(sprintf("Training set : %d rows  (%.1f%%)\n",
            nrow(train_data), 100 * nrow(train_data) / nrow(qal)))
cat(sprintf("Test set     : %d rows  (%.1f%%)\n",
            nrow(test_data),  100 * nrow(test_data)  / nrow(qal)))

# Verify class balance is preserved
cat("\nTrain progression rate:", round(mean(train_data$progressed == "Yes"), 3), "\n")
cat("Test  progression rate:", round(mean(test_data$progressed  == "Yes"), 3), "\n")
```

---

# 5. Data Preparation

```{r}
# ── A shared recipe applied to all models ────────────────────────────────────
prep_recipe <- recipe(progressed ~ ., data = train_data) %>%

  # Lump rare factor levels (< 3 % of data) into "Other"
  step_other(all_nominal_predictors(), threshold = 0.03) %>%

  # One-hot encode all categoricals (needed for XGBoost & Logistic)
  step_dummy(all_nominal_predictors(), one_hot = TRUE) %>%

  # Remove zero-variance columns created by dummy encoding
  step_zv(all_predictors()) %>%

  # Normalise numeric columns (none here, but safe to include)
  step_normalize(all_numeric_predictors())

prepped   <- prep(prep_recipe, training = train_data)
train_baked <- bake(prepped, new_data = train_data)
test_baked  <- bake(prepped, new_data = test_data)

cat("Features after pre-processing:", ncol(train_baked) - 1, "\n")
```

---

# 6. Model 1 — Logistic Regression

This is the baseline model. It gives an odds ratio revealing how each variable affects the change of progression

```{r}
# Fit on training data 
logit_fit <- glm(
  progressed ~ .,
  data   = train_baked,
  family = binomial(link = "logit")
)

# Predict probabilities on test set 
logit_prob <- predict(logit_fit, newdata = test_baked, type = "response")
logit_class <- factor(if_else(logit_prob >= 0.5, "Yes", "No"),
                      levels = c("No", "Yes"))

# Confusion matrix & basic metrics 
cm_logit <- confusionMatrix(logit_class, test_baked$progressed, positive = "Yes")
print(cm_logit)

# AUC 
roc_logit <- roc(
  response  = test_baked$progressed,
  predictor = logit_prob,
  levels    = c("No", "Yes")
)
cat(sprintf("\nLogistic Regression AUC: %.4f\n", auc(roc_logit)))
```

```{r}
# Top-20 odds ratios (actionable insight) 
or_df <- broom::tidy(logit_fit, exponentiate = TRUE, conf.int = TRUE) %>%
  filter(term != "(Intercept)") %>%
  arrange(desc(estimate)) %>%
  slice(c(1:10, (n()-9):n()))   # top 10 & bottom 10

ggplot(or_df, aes(x = reorder(term, estimate),
                  y = estimate,
                  colour = estimate > 1)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.3) +
  geom_hline(yintercept = 1, linetype = "dashed", colour = "grey") +
  coord_flip() +
  scale_colour_manual(values = c("TRUE" = "lightgreen", "FALSE" = "pink"),
                      labels = c("TRUE" = "Increases odds", "FALSE" = "Decreases odds"),
                      name   = "") +
  labs(
    title    = "Logistic Regression — Top & Bottom 10 Odds Ratios",
    subtitle = "Values > 1 increase the probability of lead progression",
    x = NULL,
    y = "Odds Ratio (exponentiated coefficient)"
  )
```

```{r}
# Full coefficient table 
broom::tidy(logit_fit, exponentiate = TRUE, conf.int = TRUE) %>%
  filter(term != "(Intercept)") %>%
  mutate(across(where(is.numeric), ~ round(.x, 4))) %>%
  arrange(p.value) %>%
  head(30) %>%
  gt() %>%
  tab_header(title = "Logistic Regression: Top 30 Significant Predictors (by p-value)") %>%
  cols_label(
    term      = "Feature",
    estimate  = "Odds Ratio",
    std.error = "Std. Error",
    statistic = "z",
    p.value   = "p-value",
    conf.low  = "95% CI Low",
    conf.high = "95% CI High"
  ) %>%
  tab_style(
    style = cell_fill(color = "lightblue"),
    locations = cells_body(rows = p.value < 0.05)
  )
```

---

# 7. Model 2 — Gradient Boosting (XGBoost)

XGBoost captures non-linear interactions between variables

```{r}
# Convert to DMatrix format 
X_train <- train_baked %>% select(-progressed) %>% as.matrix()
y_train <- as.integer(train_baked$progressed == "Yes")

X_test  <- test_baked  %>% select(-progressed) %>% as.matrix()
y_test  <- as.integer(test_baked$progressed  == "Yes")

dtrain <- xgb.DMatrix(data = X_train, label = y_train)
dtest  <- xgb.DMatrix(data = X_test,  label = y_test)
```

```{r}
# Train with cross-validated early stopping 
xgb_params <- list(
  objective         = "binary:logistic",
  eval_metric       = "auc",
  eta               = 0.05,         
  max_depth         = 5,
  subsample         = 0.80,
  colsample_bytree  = 0.80,
  min_child_weight  = 10,
  gamma             = 1
)

set.seed(42)
xgb_cv <- xgb.cv(
  params    = xgb_params,
  data      = dtrain,
  nrounds   = 500,
  nfold     = 5,
  early_stopping_rounds = 30,
  verbose   = 0,
  prediction = FALSE
)

best_nrounds <- xgb_cv$niter
if (!is.null(xgb_cv$evaluation_log) && "test_auc_mean" %in% names(xgb_cv$evaluation_log)) {
  best_nrounds <- which.max(xgb_cv$evaluation_log$test_auc_mean)
}

best_nrounds <- as.integer(best_nrounds)

cat(sprintf("Best number of rounds (CV): %d\n", best_nrounds))

xgb_fit <- xgb.train(
  params  = xgb_params,
  data    = dtrain,
  nrounds = best_nrounds,
  verbose = 0
)
```

```{r}
# Predict & evaluate 
xgb_prob  <- predict(xgb_fit, dtest)
xgb_class <- factor(if_else(xgb_prob >= 0.5, "Yes", "No"),
                    levels = c("No", "Yes"))

cm_xgb <- confusionMatrix(xgb_class,
                           factor(if_else(y_test == 1, "Yes", "No"),
                                  levels = c("No","Yes")),
                           positive = "Yes")
print(cm_xgb)

roc_xgb <- roc(
  response  = y_test,
  predictor = xgb_prob
)
cat(sprintf("\nXGBoost AUC: %.4f\n", auc(roc_xgb)))
```

```{r}
# Feature importance 
xgb_imp <- xgb.importance(
  feature_names = colnames(X_train),
  model         = xgb_fit
)

xgb_imp %>%
  slice_head(n = 25) %>%
  ggplot(aes(x = reorder(Feature, Gain), y = Gain)) +
  geom_col(fill = "orange") +
  coord_flip() +
  labs(
    title    = "XGBoost — Top 25 Features by Gain",
    subtitle = "Gain = average improvement in loss when a feature is used to split",
    x = NULL,
    y = "Gain"
  )
```

---

# 8. Model 3 — Random Forest

Random Forest is stable and handles lots of variables well 

```{r}
# Fit (500 trees, default mtry = sqrt(p))
train_baked[is.na(train_baked)] <- 0


set.seed(42)
rf_fit <- randomForest(
  progressed ~ .,
  data       = train_baked,
  ntree      = 500,
  importance = TRUE,
  classwt    = c("No" = 1, "Yes" = 4)  
)

print(rf_fit)
```

```{r}
# Predict & evaluate 
rf_prob  <- predict(rf_fit, newdata = test_baked, type = "prob")[, "Yes"]
rf_class <- predict(rf_fit, newdata = test_baked, type = "class")

cm_rf <- confusionMatrix(rf_class, test_baked$progressed, positive = "Yes")
print(cm_rf)

roc_rf <- roc(
  response  = test_baked$progressed,
  predictor = rf_prob,
  levels    = c("No", "Yes")
)
cat(sprintf("\nRandom Forest AUC: %.4f\n", auc(roc_rf)))
```

```{r}

rf_imp_df <- data.frame(
  Feature   = rownames(importance(rf_fit)),
  MeanDecreaseGini = importance(rf_fit)[, "MeanDecreaseGini"]
) %>%
  arrange(desc(MeanDecreaseGini)) %>%
  slice_head(n = 25)

ggplot(rf_imp_df, aes(x = reorder(Feature, MeanDecreaseGini),
                      y = MeanDecreaseGini)) +
  geom_col(fill = "lightgreen") +
  coord_flip() +
  labs(
    title    = "Random Forest — Top 25 Features by Mean Decrease in Gini",
    subtitle = "Higher values = greater contribution to splitting purity",
    x = NULL,
    y = "Mean Decrease Gini"
  )
```

---

# 9. Model Comparison & ROC Curves

```{r}
# Overlay all three ROC curves 
ggroc(
  list(
    "Logistic Regression" = roc_logit,
    "XGBoost"             = roc_xgb,
    "Random Forest"       = roc_rf
  ),
  legacy.axes = TRUE,
  size = 1
) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed",
              colour = "grey") +
  scale_colour_manual(
    values = c(
      "Logistic Regression" = "pink",
      "XGBoost"             = "orange",
      "Random Forest"       = "lightgreen"
    )
  ) +
  annotate("text", x = 0.65, y = 0.20,
           label = sprintf(
             "AUC\nLogit : %.3f\nXGBoost: %.3f\nRF     : %.3f",
             auc(roc_logit), auc(roc_xgb), auc(roc_rf)
           ),
           hjust = 0, size = 4, family = "mono") +
  labs(
    title   = "ROC Curve Comparison — All Three Models",
    x       = "False Positive Rate (1 – Specificity)",
    y       = "True Positive Rate (Sensitivity)",
    colour  = "Model"
  )
```

```{r}
# Side-by-side performance table 
extract_metrics <- function(cm, roc_obj, model_name) {
  data.frame(
    Model      = model_name,
    AUC        = round(as.numeric(auc(roc_obj)), 4),
    Accuracy   = round(cm$overall["Accuracy"], 4),
    Precision  = round(cm$byClass["Precision"], 4),
    Recall     = round(cm$byClass["Recall"], 4),
    F1         = round(cm$byClass["F1"], 4),
    Specificity = round(cm$byClass["Specificity"], 4)
  )
}

metrics_df <- bind_rows(
  extract_metrics(cm_logit, roc_logit, "Logistic Regression"),
  extract_metrics(cm_xgb,   roc_xgb,   "XGBoost"),
  extract_metrics(cm_rf,    roc_rf,    "Random Forest")
)

metrics_df %>%
  gt() %>%
  tab_header(title = "Model Performance Summary — Test Set") %>%
  fmt_number(columns = -Model, decimals = 4) %>%
  tab_style(
    style = list(cell_fill(color = "lightblue"),
                 cell_text(weight = "bold")),
    locations = cells_body(
      rows = AUC == max(AUC)
    )
  )
```

---

# 10. Calibration Plot (Best Model)

This checks how well predicted probabilities match reality. Can we trust the scores?

```{r}
# uses the best performing model
best_prob <- xgb_prob
best_actual <- y_test

cal_df <- data.frame(
  prob   = best_prob,
  actual = best_actual
) %>%
  mutate(bin = cut(prob, breaks = seq(0, 1, by = 0.1),
                   include.lowest = TRUE)) %>%
  group_by(bin) %>%
  summarise(
    mean_pred  = mean(prob),
    mean_actual = mean(actual),
    n          = n(),
    .groups    = "drop"
  )

ggplot(cal_df, aes(x = mean_pred, y = mean_actual)) +
  geom_point(aes(size = n), colour = "orange") +
  geom_line(colour = "orange") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed",
              colour = "grey") +
  scale_size_continuous(name = "N in bin") +
  labs(
    title    = "Calibration Plot — XGBoost",
    subtitle = "Points near the diagonal indicate well-calibrated probabilities",
    x = "Mean Predicted Probability",
    y = "Observed Progression Rate"
  )
```

---

# 11. Threshold Optimisation

The default 0.50 threshold maximizes accuracy.
But for sales, we check

Lower threshold → catch more good leads (higher recall)
Higher threshold → fewer false positives (higher precision)

We test different thresholds to find the best balance.

```{r}
# Precision-Recall tradeoff for XGBoost 
thresholds <- seq(0.10, 0.70, by = 0.05)

thresh_df <- purrr::map_dfr(thresholds, function(t) {
  pred_class <- factor(if_else(xgb_prob >= t, "Yes", "No"),
                       levels = c("No", "Yes"))
  actual     <- factor(if_else(y_test == 1, "Yes", "No"),
                       levels = c("No", "Yes"))
  cm         <- confusionMatrix(pred_class, actual, positive = "Yes")
  data.frame(
    Threshold  = t,
    Precision  = cm$byClass["Precision"],
    Recall     = cm$byClass["Recall"],
    F1         = cm$byClass["F1"],
    Specificity = cm$byClass["Specificity"]
  )
})

thresh_long <- thresh_df %>%
  pivot_longer(-Threshold, names_to = "Metric", values_to = "Value")

ggplot(thresh_long, aes(x = Threshold, y = Value, colour = Metric)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  scale_colour_manual(values = c(
    Precision   = "lightgreen",
    Recall      = "pink",
    F1          = "orange",
    Specificity = "lightblue"
  )) +
  labs(
    title    = "XGBoost — Precision / Recall / F1 Across Decision Thresholds",
    subtitle = "Lower threshold → higher recall; higher threshold → higher precision",
    x = "Classification Threshold",
    y = "Metric Value",
    colour = "Metric"
  )

# Highlight the F1-optimal threshold
best_thresh_row <- thresh_df %>%
  filter(!is.na(F1)) %>%
  slice_max(F1, n = 1)
cat(sprintf("F1-optimal threshold: %.2f  (Precision=%.3f, Recall=%.3f, F1=%.3f)\n",
            best_thresh_row$Threshold,
            best_thresh_row$Precision,
            best_thresh_row$Recall,
            best_thresh_row$F1))
```

---

# 12. Lead Scoring & Actionable Segments

We use the best model to score every lead.

```{r}
# score the full dataset 
full_baked <- bake(prepped, new_data = qal)
X_full     <- full_baked %>% select(-progressed) %>% as.matrix()

qal_scored <- qal %>%
  mutate(
    progression_score = predict(
      xgb_fit,
      xgb.DMatrix(data = X_full)
    ),
    score_tier = case_when(
      progression_score >= 0.40 ~ "Hot   (≥40%)",
      progression_score >= 0.25 ~ "Warm  (25–40%)",
      progression_score >= 0.15 ~ "Lukewarm (15–25%)",
      TRUE                      ~ "Cold  (<15%)"
    )
  )

qal_scored %>%
  count(score_tier) %>%
  mutate(pct = scales::percent(n / sum(n), accuracy = 0.1)) %>%
  gt() %>%
  tab_header(title = "Lead Score Distribution — Full Dataset")
```

```{r}
# Mean score by key segments 
seg_mfg <- qal_scored %>%
  group_by(acct_manufacturing_model) %>%
  summarise(
    n             = n(),
    mean_score    = mean(progression_score),
    actual_rate   = mean(progressed == "Yes"),
    .groups = "drop"
  ) %>%
  arrange(desc(mean_score))

p1 <- ggplot(seg_mfg,
       aes(x = reorder(acct_manufacturing_model, mean_score),
           y = mean_score)) +
  geom_col(fill = "lightgreen") +
  geom_text(aes(label = scales::percent(mean_score, accuracy = 0.1)),
            hjust = -0.1, size = 3.5) +
  coord_flip() +
  scale_y_continuous(limits = c(0, 0.45)) +
  labs(title = "Mean Progression Score\nby Manufacturing Model",
       x = NULL, y = "Mean Score")

seg_func <- qal_scored %>%
  group_by(function_band) %>%
  summarise(
    n          = n(),
    mean_score = mean(progression_score),
    .groups    = "drop"
  ) %>%
  arrange(desc(mean_score))

p2 <- ggplot(seg_func,
       aes(x = reorder(function_band, mean_score),
           y = mean_score)) +
  geom_col(fill = "orange") +
  geom_text(aes(label = scales::percent(mean_score, accuracy = 0.1)),
            hjust = -0.1, size = 3.5) +
  coord_flip() +
  scale_y_continuous(limits = c(0, 0.45)) +
  labs(title = "Mean Progression Score\nby Functional Area",
       x = NULL, y = "Mean Score")

grid.arrange(p1, p2, ncol = 2)
```

```{r top-segment-table}
# ICP Cluster Table 
qal_scored %>%
  filter(solution_rollup == "Mx") %>%
  group_by(acct_manufacturing_model, acct_tier_rollup, function_band) %>%
  summarise(
    n              = n(),
    mean_score     = round(mean(progression_score), 3),
    actual_rate    = round(mean(progressed == "Yes"), 3),
    .groups        = "drop"
  ) %>%
  filter(n >= 50) %>%
  arrange(desc(mean_score)) %>%
  slice_head(n = 20) %>%
  gt() %>%
  tab_header(
    title    = "Top Mx ICP Clusters — Manufacturing Model × Tier × Function",
    subtitle = "Ranked by mean predicted progression score (min. 50 leads)"
  ) %>%
  fmt_number(columns = c(mean_score, actual_rate), decimals = 3) %>%
  tab_style(
    style     = cell_fill(color = "lightblue"),
    locations = cells_body(rows = mean_score >= 0.30)
  )
```

---

# 13. Mx vs Qx Progression Score Comparison
Qx leads generally have higher scores overall
Mx still has strong opportunities, especially in high-scoring segments

```{r}
qal_scored %>%
  filter(solution_rollup %in% c("Mx", "Qx")) %>%
  ggplot(aes(x = progression_score, fill = solution_rollup)) +
  geom_density(alpha = 0.55) +
  scale_fill_manual(values = c("Mx" = "orange", "Qx" = "lightgreen")) +
  scale_x_continuous(labels = scales::percent) +
  labs(
    title    = "Predicted Progression Score Distribution: Mx vs Qx",
    subtitle = "Qx distribution shifted right confirms stronger baseline; Mx has opportunity in right tail",
    x        = "Predicted Progression Probability",
    y        = "Density",
    fill     = "Product"
  )
```

# Mx Targeting Strategy

```{r mx-targeting-playbook, message=FALSE, warning=FALSE}
# Create actionable Mx targeting strategy based on model results

# Analyze Mx segments by key characteristics
mx_segments <- qal_scored %>%
  filter(solution_rollup == "Mx") %>%
  group_by(acct_manufacturing_model, acct_tier_rollup) %>%
  summarise(
    n_leads = n(),
    avg_score = mean(progression_score),
    actual_rate = mean(progressed == "Yes"),
    .groups = "drop"
  ) %>%
  filter(n_leads >= 30) %>%  # Minimum sample size
  arrange(desc(avg_score))

# Show top and bottom segments
cat("=== MX TARGETING PLAYBOOK ===\n\n")
cat("HIGH-PRIORITY MX SEGMENTS (Target These):\n")

top_5 <- mx_segments %>%
  slice_head(n = 5) %>%
  mutate(
    avg_score = scales::percent(avg_score, accuracy = 0.1),
    actual_rate = scales::percent(actual_rate, accuracy = 0.1)
  )

print(as.data.frame(top_5), row.names = FALSE)

cat("\n\nLOW-PRIORITY MX SEGMENTS (Avoid These):\n")

bottom_5 <- mx_segments %>%
  slice_tail(n = 5) %>%
  mutate(
    avg_score = scales::percent(avg_score, accuracy = 0.1),
    actual_rate = scales::percent(actual_rate, accuracy = 0.1)
  )

print(as.data.frame(bottom_5), row.names = FALSE)

# Calculate improvement potential
high_priority <- qal_scored %>%
  filter(solution_rollup == "Mx",
         progression_score >= 0.18)  # Above baseline threshold

all_mx <- qal_scored %>%
  filter(solution_rollup == "Mx")

cat("\n\n=== EXPECTED IMPACT ===\n")
cat("Current Mx baseline:", scales::percent(mean(all_mx$progression_score), accuracy = 0.1), "\n")
cat("High-priority segments (>18% predicted):", 
    scales::percent(mean(high_priority$progression_score), accuracy = 0.1), "\n")
cat("Number of high-priority leads:", nrow(high_priority), 
    "out of", nrow(all_mx), 
    paste0("(", round(100*nrow(high_priority)/nrow(all_mx), 1), "%)"), "\n")
cat("Improvement potential: +", 
    round((mean(high_priority$progression_score) - mean(all_mx$progression_score)) * 100, 1),
    "percentage points\n")
```
Mx Targeting Strategy: 

Clear winners: Small companies with CMO/CDMO or In-House models (20-24% predicted). 

Clear losers: Services, Software, Research companies (<7% predicted) - not actual manufacturers.

Bottom line: Only 23.5% of Mx leads are high-priority (>18% predicted). Focusing on these improves Mx from 12.4% baseline to ~35%.

For SDRs: Target CMO/CDMO + Small and In-House + Small. Avoid Services/Software segments.

---

# 14. Key Findings & Actionable Recommendations
This modeling helped to uncover lead progression using prediction on the available data. Out of the different models explored, XGBoost performed the best. logistic regression helped with the interpretation. 

The most important factor is the manufacturing model (how a company produces products) as it directly shows a company's need for the product. Account tier, job function, and seniority also help identify leads. 

Limitations of this modeling include:
Limited data quality - some variables have missing values or used heavy cleaning reducing accuracy
class imbalance- ~15% of leads actually progress, so model may struggle to correctly identify all positive cases
over fitting - may not totally generalize 
xgboost is not as explainable as logistic regression
no changes over time are captured in the model


#AI LOG
AI was used to help formulate and debug coding, especially for the figures used. 
Some help was sought confirming output interpretation

